---
title: "Chapter01"
output: html_notebook
---
NOTE:
1. R uses 1 based indexing
2. R uses double mod sign for mod (%%)


Some functions work with strings

```{r}
lang.domain <- 'Statistics'
```
Let's change it to uppercase

```{r}
lang.domain <- toupper(lang.domain)
lang.domain
```
Retrieve substring from first character to fourth character 
```{r}
substr(lang.domain, 1, 4)
```
Substitute every "I" for "Y"
```{r}
gsub('I', 'Y', lang.domain)
```
Combine character strings
```{r}
X <- paste('R does', lang.domain, '!!!')
X
```
FLOW OF CONTROL
________________
The most basic flow of control construct is the if statement. The argument to 
an if statement (what goes between the parentheses) is an expression that 
returns a logical value. The block of code following the if statement gets 
executed only if the expression yields TRUE:
```{r}
if(2 == 2)
  print('True')
```
It is possible to execute more than one statement if an if condition is 
triggered; you just have to use curly brackets ({}) 
```{r}
if((4/2 == 2) & (8/4 == 2)){
  print('4/2 == 2')
  print('8/4 == 2')
}
```

It is also possible to specify a block of code that will get executed if the 
if conditional is FALSE:
```{r}
if(5 %% 2 == 0){
  print('Moded!')
}else{
  print('Unmoded!')
}
```
```{r}
closing.time <- TRUE
if(closing.time){
  print('It\'s time to go home.')
}else{
  print('You can still stay here')
}

closing.time <- 0

if(!closing.time){
  print('We still have some work time')
}else{
  print('We gotta go, it\'s closing time!')
}
```

























